---
title: "Vignette for BMIthreshcount package"
author: "Mingwei Tang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

 This is a R package doing statistical inference gaining counting the number of gaining traits during evolution. The model is based on phlyogenetic stochastic mapping and using Brownian motion interval crossing model for binary trait transition. With the help of `BMI_thresh`, we can do fellowing things

- Calculating prior and posterior probabilities for interval crossing on a single line
- Calculating prior and posterior probability for crossing numbers on a given phylogenetic tree
- Run Calibrated Brownian motion method (CBM) to get the bayes factors and results on test the transition numbers

```{r setup,include=F}
library(BMIthreshCount)
```
## Brownian motion interval crossing model
# simulate a Brown motion path and plot
```{r,figure.show='hold'}
set.seed(223)
# simulate a Brown motion path and plot
OUpath(1,1,1000,0,1,pl = T)
```
## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output:
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
